### 2018-12-12 chapters/3-results.tex
table grooming

\begin{table}[!h]
  \caption{Texture methods ranked in the best one percent.}%
  \label{tab:texture_best1p}

@@

\begin{table}[!h]
  \caption{Best texture feature per image type.}%
  \label{tab:texture_imagetype}

@@

\begin{table}[!h]
  \caption{Best statistical feature per image type.}%
  \label{tab:stats_imagetype}

@@

\begin{table}[!h]
  \caption{Area under the receiver operating curve values estimated using outer
  leave-pair-out cross-validation (LPOCV) per image type with all features, top
  1\% features filtered by AUC, and the 18 statistical features.}%
  \label{tab:auc_imagetype}

@@

\begin{table}[!h]
  \caption{Area under the receiver operating curve values estimated using outer
  leave-pair-out cross-validation (LPOCV) for the combinations of the image
  types.}%
  \label{tab:auc_combinations}

>>>>

\begin{table}[!h]
  \centering
  \caption{{\bf Texture methods ranked in the best one percent.}}%
  \label{tab:texture_best1p}

@@

\begin{table}[!h]
  \centering
  \caption{{\bf Best texture feature per image type.}}%
  \label{tab:texture_imagetype}

@@

\begin{table}[!h]
  \centering
  \caption{{\bf Best statistical feature per image type.}}%
  \label{tab:stats_imagetype}

@@

\begin{table}[!h]
  \centering
  \caption{{\bf Area under the receiver operating curve values estimated using
  outer leave-pair-out cross-validation (LPOCV) per image type with all
  features, top 1\% features filtered by AUC, and the 18 statistical
  features.}}%
  \label{tab:auc_imagetype}

@@

\begin{table}[!h]
  \centering
  \caption{{\bf Area under the receiver operating curve values estimated using
  outer leave-pair-out cross-validation (LPOCV) for the combinations of the
  image types.}}%
  \label{tab:auc_combinations}
